---
title: "Mudcrabs DGE Analysis"
---
Main references :   
1. http://bioconductor.org/packages/devel/bioc/vignettes/DESeq2/inst/doc/DESeq2.html  
2. https://github.com/hbctraining/DGE_workshop/tree/master/lessons  

First time setup:
```
install.packages("renv")   # Step 1: In R console, please install `renv` package

                           # Step 2: Open .Rproj, or if already open, restart R session

renv::restore()            # Step 3: Run this
```

# STEP 1 - Prepare DESeq dataset using txImport
```{r message=FALSE}
loadDependencies()
DIR_RSEM <- "data/counts_per_sample"
dseq_orig <- importRSEM(DIR_RSEM, reload = TRUE)
```

# STEP 2 - Filter Genes and Samples
```{r}
df_annot.orig <- read.csv("data/annotation.20200701.csv", stringsAsFactors = FALSE)
annotSignif <- 1e-10
alnLenThreshold <- 50

df_annot <- df_annot.orig %>% filter(fly_stat_sig < annotSignif & fly_len_perc >= alnLenThreshold )

df_annot_uniq <- df_annot %>% distinct(gene_id, .keep_all = TRUE)

dseq <- filter.genes(dseq_orig, df_annot) %>%
        filter.samples(c("BAT_E_2", "CAG_C_3", "CAG_E_1", "BIC_C_3"))

filter.printSummary(dseq)
# plotGene_Distribution(dseq, save = FALSE)
```

```{r}
dseq_qc <- qcPrepare(dseq)

qc.setSaveImg(TRUE)

dseq_qc %>% 
    qc.plotGene_MeanSD() %>% 
    qc.plotGene_Heatmap() %>% 
    qc.plotSample_ClusterHeatmap(subsetByLocation = TRUE, subsetBySampleGrps = TRUE) %>% 
    qc.plotSample_ClusterDendrograms() %>% 
    qc.plotSample_PCA(factors = c("location", "condition"))
```

#  NB model fitting W/ significance testing
Full Model w/ Reference level CAG C
Intercept + E + BIC + BAT + BIC.E + BAT.E

H0 : There is no significant difference between (CAG_C - CAG_E) - (BAT_C - BAT_E)
    E - (E + BAT.E) = 0
    BAT.E = 0

H0 : There is no significant difference between (CAG_C - CAG_E) - (BIC_C - BIC_E)
    E - (E + BIC.E) = 0
    BIC.E = 0
    
H0 : There is no significant difference between (BAT_C - BAT_E) - (BIC_C - BIC_E)
    (E + BAT.E) - (E + BIC.E) = 0
    BAT.E - BIC.E = 0
    
H0 : There is no significant difference between (CAG_C - CAG_E)
    E = 0
    
H0 : There is no significant difference between (BAT_C - BAT_E)
    E + BAT.E = 0
    
H0 : There is no significant difference between (BIC_C - BIC_E)
    E + BIC.E = 0

```{r }
mainEffects <- list(testIDs = c("E", "E + BAT.E", "E + BIC.E"),
                   labels = c("CAG", "BAT", "BIC"))

interEffects <- list(testIDs = c("BAT.E", "BIC.E", "BAT.E - BIC.E"),
                   labels = c("CAG vs BAT", "CAG vs BIC", "BAT vs BIC"))

fitted <- deg.signifTest(dseq, testIds = c(mainEffects[['testIDs']], interEffects[['testIDs']]), signif = 0.1) %>% 
          deg.addColumn_InterCategory(interEffects[['testIDs']])
```
```{r}
setTimestampNow()
deg.setSaveImg(TRUE)

# Export degenes to CSV
df_isDesc <- read.csv(getPath_fromProjWd("supplementary notebooks/results/Stress Reponse Genes (fly_acc)/geneID_isDescendant.csv"))

listColumns <- c("fly", "fly_acc", "isDescendant")

deg.exportDEGenes(fitted, merge(df_annot_uniq, df_isDesc, by="gene_id", all.x = TRUE), 
                  extractCols = listColumns, outDirSuffix = " (unique)")

deg.exportDEGenes(fitted, merge(df_annot, df_isDesc, by="gene_id", all.x = TRUE), 
                  extractCols = listColumns, outDirSuffix = " (w duplicates)")
```

```{r}
# Main Effects 

fitted %>% 
    deg.plot_ReadCounts(mainEffects, labelFrom_df = df_annot_uniq, labelFrom_column = "fly") %>% 
    deg.plot_VennDiagram2(mainEffects, subtitle = " (Main Effect)") %>% 
    deg.plot_BarGraph(mainEffects) %>% 
    deg.plot_MA(mainEffects, df_isDesc)
```

```{r}
# Interaction Effects
fitted %>% 
  deg.plot_VennDiagram2(interEffects, subtitle = " (Interaction Effect)") %>%
  deg.plotInter_CategoryTable(interEffects) %>% 
  deg.plotInter_Heatmap(interEffects, df_isDesc = df_isDesc) %>% 
  deg.plotInter_LfcDifference(interEffects)

deg.plotInteractionPlot_Multiple(fitted, interEffects, orderby = "lfc", 
                                 labelFrom_df = df_annot, labelFrom_column = "fly_acc",
                                 df_isDesc = df_isDesc)

# deg.plotInteractionPlot_Multiple(fitted, interEffects, orderby = "padj",
#                                  labelFrom_df = df_annot, labelFrom_column = "fly_acc",
#                                  f_isDesc = df_isDesc)
```

```{r}
# Figure 2 - Interaction Effects
deg.setSaveImg(FALSE)
interEffects <- list(testIDs = c("BAT.E", "BIC.E"),
                   labels = c("CAG vs BAT", "CAG vs BIC"))

df_isDesc <- read.csv(getPath_fromProjWd("supplementary notebooks/results/Stress Reponse Genes (fly_acc)/geneID_isDescendant.csv"))
# p1 <- deg.plot_VennDiagram2(fitted, interEffects, padding = 0.2, scale=0.8, label_textSize = 6, returnPlot = TRUE)
# p2 <- deg.plotInter_CategoryTable(fitted, interEffects, returnPlot = TRUE)
p3 <- deg.plotInter_Heatmap(fitted, interEffects, df_isDesc=df_isDesc, returnPlot = TRUE)

# Convert ComplexHeatmap to grob
p3_grob <- lapply(p3, function(x){ 
                grid.grabExpr(draw(x, annotation_legend_side="top"))
              })

# Arrange plots into rows
# plot_ab <- plot_grid(p1, p2, nrow = 1, labels=c("(a)", "(b)"))
# plot_cd <- plot_grid(NULL, p3_grob[[1]],NULL, p3_grob[[2]], NULL, nrow=1, labels=c("","(c)","","(d)",""), label_x = -0.03, rel_widths = c(0.1,0.35,0.1,0.35,0.1))
plot_ab <- plot_grid(p3_grob[[1]], NULL, p3_grob[[2]], nrow=1, labels=c("(a)", "", "(b)"), rel_widths = c(.49, .01, .49))

# Combine plots into one
# combinedPlot <- plot_grid(plot_ab, NULL, plot_cd, ncol=1, rel_heights = c(1,0.1, 2.2))
savePlot(plot_ab, width = 13, height = 6,
         filedir = deg.getResultDir("Visualization/Combined"), 
         filename = "Figure 2 - Interaction Effects")
```
```{r}
# Figure 3

deg.setSaveImg(FALSE)
p1 <- deg.plot_VennDiagram2(fitted, mainEffects, scale = 0.6, returnPlot = TRUE)
p2 <- deg.plot_BarGraph(fitted, mainEffects, returnPlot = TRUE)
p3 <- deg.plot_MA(fitted, mainEffects, df_isDesc = df_isDesc, returnPlot = TRUE)

# Increase font size in Bar Graph 
p2 <- p2 + theme(legend.text = element_text(size=12), axis.text.y = element_text(size=12))

# Create shared legend, X axis title, and Y axis title for the 3 MA plots
p3_legend <- get_legend(p3[[1]] + 
                        theme(legend.text = element_text(size=12), legend.position = "bottom") +
                        guides(color=guide_legend(reverse=TRUE, nrow = 1, override.aes=list(size=4))))
# p3_axisTitle_X <- textGrob(p3[[1]]$labels$x, gp=gpar(fontsize=14))
# p3_axisTitle_Y <- textGrob(p3[[1]]$labels$y, gp=gpar(fontsize=14), rot=90)

# Remove legends for each individual MA plot
p3_temp <- list()
for(i in 1:length(p3)){
  p3_temp[[i]] <- p3[[i]] + 
    labs(subtitle = mainEffects[['labels']][[i]],  title= "") +
    theme(legend.position = "None",
          plot.subtitle = element_text(hjust=0.5))
  # if(i != 1){
  #   p3_temp[[i]] <- p3_temp[[i]] + theme(axis.title = element_blank())
  # }
}
p3_noLegend <- plot_grid(p3_temp[[2]],p3_temp[[3]],  nrow = 1, labels=c("(c)","(d)"))

# Arrange plots into rows
# plot_ab <- plot_grid(p1, p2, nrow = 1, labels=c("(a)", "(b)"))

# Combine all plots into one
# combinedPlot <- plot_grid(plot_ab,NULL,plot_cde,
#                           ncol=1, rel_heights = c(0.3, 0.05, 0.6))

combinedPlot <- plot_grid(p2 + theme(legend.position = "top", legend.title = element_blank()), 
                          p3_temp[[1]], p3_temp[[2]],p3_temp[[3]], 
                          ncol = 2, nrow = 2, labels = c("(a)", "(b)", "(c)", "(d)"))

combinedPlot2 <- plot_grid(combinedPlot, p3_legend, ncol = 1, rel_heights = c(1, .1))

savePlot(combinedPlot2, width=7, height=7,
         filedir = deg.getResultDir("Visualization/Combined"),
         filename = "Figure 3 - Main Effects")
```

```{r}
# Figure Top 20 read counts

deg.setSaveImg(FALSE)
p <- deg.plot_ReadCounts(fitted, mainEffects, labelFrom_df = df_annot_uniq,
                         labelFrom_column = "fly_acc", returnPlot = TRUE)

p_title <- textGrob(p[[1]]$labels$title, gp=gpar(fontsize=16))

# Create a shared legend, axis title X and Y
p_axisTitle_X <- textGrob(p[[1]]$labels$x, gp=gpar(fontsize=10))
p_axisTitle_Y <- textGrob(p[[1]]$labels$y, gp=gpar(fontsize=10),rot = 90)
p_legend <- get_legend(p[[1]] + 
                         theme(legend.position="bottom", legend.text = element_text(size=14)) + 
                         guides(color=guide_legend(nrow = 1)))

# Remove individual legends
p_temp <- list()
for(i in 1:length(p)){
  p_temp[[i]] <- p[[i]] + theme(legend.position="None", 
                                plot.subtitle = element_text(hjust = 0.5, size = 14), 
                                axis.title = element_blank(), 
                                axis.text.x = element_text(size=8)) + 
                          labs(subtitle=mainEffects[['labels']][[i]], title="")
}

# Combine axis title X and Y to all the plots
plot_abc <- arrangeGrob(plot_grid(p_temp[[1]], p_temp[[2]], p_temp[[3]], nrow=1), 
                                      left = p_axisTitle_Y, bottom = p_axisTitle_X, top = p_title)

# Then, combine the legend
combinedPlot <- plot_grid(plot_abc, p_legend, ncol=1, rel_heights = c(0.9, 0.1))
savePlot(combinedPlot, width = 10, height = 5,
         filedir = deg.getResultDir("Visualization/Combined"),
         filename = "Figure - Read Counts")
```





