---
title: "2a. Fruit fly only (10e^-5) "

output: html_notebook
---
<p style="text-align:center;"><b>Initial Count</b></p>

<style type="text/css">
.tg  {border:none;border-collapse:collapse;border-spacing:0;}
.tg td{border-style:solid;border-width:0px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;
  padding:7px 15px;word-break:normal;}
.tg th{border-style:solid;border-width:0px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;
  overflow:hidden;padding:7px 15px;word-break:normal;}
.tg .tg-73oq{border-color:#000000;text-align:left;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-73oq">Total number of genes</th>
    <th class="tg-73oq">17690</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-73oq">After filtering, the number of descendant genes is</td>
    <td class="tg-73oq"><span style="font-weight:bold;color:#2B86FF">3132 Desc</span></td>
  </tr>
  <tr>
    <td class="tg-73oq">After fitting, the number of outliers is</td>
    <td class="tg-73oq"><span style="color:#FF3838">8 Desc</span> out of 69</td>
  </tr>
</tbody>
</table>
 

<p style="text-align:center;"><b>Differential Analysis Results</b></p>
<style type="text/css">
.tg  {border:none;border-collapse:collapse;border-spacing:0;}
.tg td{border-style:solid;border-width:0px;font-family:Arial, sans-serif;font-size:14px;overflow:hidden;
  padding:10px 5px;word-break:normal;}
.tg th{border-style:solid;border-width:0px;font-family:Arial, sans-serif;font-size:14px;font-weight:normal;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-65px{background-color:#ecf4ff;border-color:#000000;text-align:left;vertical-align:top}
.tg .tg-7btt{border-color:inherit;font-weight:bold;text-align:center;vertical-align:top}
.tg .tg-0pky{border-color:inherit;text-align:left;vertical-align:top}
.tg .tg-73oq{border-color:#000000;text-align:left;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-0pky"></th>
    <th class="tg-7btt">BAT.E</th> 
    <th class="tg-7btt">BIC.E</th> 
    <th class="tg-7btt">BAT.E - BIC.E</th> 
    <th class="tg-7btt">E</th> 
    <th class="tg-7btt">E + BAT.E</th> 
    <th class="tg-7btt">E + BIC.E</th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-73oq">Removed by Ind. Filtering</td>
    <td class="tg-73oq"><span style="color:#FF3838">2037 Desc</span><br><span style="font-style:italic">out of 10582</span></td> 
    <td class="tg-73oq"><span style="color:#FF3838">1623 Desc</span><br><span style="font-style:italic">out of 8374</span></td> 
    <td class="tg-73oq"><span style="color:#FF3838">2199 Desc</span><br><span style="font-style:italic">out of 11536</span></td> 
    <td class="tg-73oq"><span style="color:#FF3838">1872 Desc</span><br><span style="font-style:italic">out of 9633</span></td> 
    <td class="tg-73oq"><span style="color:#FF3838">1872 Desc</span><br><span style="font-style:italic">out of 9633</span></td> 
    <td class="tg-73oq"><span style="color:#FF3838">1739 Desc</span><br><span style="font-style:italic">out of 9012</span></td>
  </tr>
  <tr>
    <td class="tg-73oq">Final descendants for testing&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;</td>
    <td class="tg-73oq">1087 Desc</td> 
    <td class="tg-73oq">1501 Desc</td> 
    <td class="tg-73oq">925 Desc</td> 
    <td class="tg-73oq">1252 Desc</td> 
    <td class="tg-73oq">1252 Desc</td> 
    <td class="tg-73oq">1385 Desc</td>
  </tr>
  <tr>
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">Signif. DE genes</span></td>
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">83 Desc</span><br><span style="font-style:italic">out of 570</span></td> 
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">23 Desc</span><br><span style="font-style:italic">out of 153</span></td> 
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">42 Desc</span><br><span style="font-style:italic">out of 211</span></td> 
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">36 Desc</span><br><span style="font-style:italic">out of 265</span></td> 
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">174 Desc</span><br><span style="font-style:italic">out of 1118</span></td> 
    <td class="tg-65px"><span style="font-weight:bold;color:#2B86FF">54 Desc</span><br><span style="font-style:italic">out of 307</span></td>
  </tr>
  <tr>
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">Overrepresented Test</span></td>
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">pval = 0.976</span></td> 
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">pval = 0.7745</span></td> 
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">pval = 0.1747</span></td> 
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">pval = 0.9578</span></td> 
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">pval = 0.9725</span></td> 
    <td class="tg-0pky"><span style="font-style:italic;color:#AAA">pval = 0.485</span></td>
  </tr>
</tbody>
</table>
   
   
```{r, echo=FALSE, results='asis', message=FALSE}
filtered <- filterData(dseq_orig, 
                        samples = c("BAT_E_2", "CAG_C_3", "CAG_E_1", "BIC_C_3"),
                        filtername = "annot", verbose = FALSE,
                        args=list(
                          signif = 10e-05, 
                          dbNames = c("fly")))
fitted <- modelfit(filtered)
fitted <- signifTest(fitted, testIds = list("BAT.E", "BIC.E", "BAT.E - BIC.E", "E", "E + BAT.E", "E + BIC.E"))

fitted <- trackDescGenes(filtered = filtered, fitted = fitted)
```


```{r, echo=FALSE, results='hide'}
exportDEgenes(fitted, dbNames = c("fly"))
```

